### 2020-04-23 README.Rmd
vignette test2
readme links

Details on the other functions and the datasets can be found in the [vignette](vignette_how_to.html) of the package.

@@

>>>>

Details on the other functions and the datasets can be found in the vignette of the package `vignette("v_covid19census")`.

@@

### Terms of Use

Refer to the [License](https://github.com/c1au6i0/covid19census/blob/master/LICENSE.md) for details on the terms of use and copyrights.
